%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
\cvsubsection{Peer-Reviewed Journal Papers (1\textsuperscript{st}, 2\textsuperscript{nd} \& 3\textsuperscript{rd})}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvhonors}

%---------------------------------------------------------
  \cvhonor
    {F. Danieli, \textbf{T. Demarcy}, M. S. A. do Amaral, [\ldots] and M. A. Hyppolito.  \textit{Auditory Performance of Post-Lingually Deafened Adult Cochlear Implant Recipients Using Electrode Deactivation Based on Postoperative Cone Beam CT Images}. European Archives of Oto-Rhino-Laryngology, 2020.} % Award
    {\hypertarget{DDA+20}{[DDA+20]}} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\textbf{T. Demarcy}, Z. Wang, C. Vandersteen, [\ldots] and H. Delingette.  \textit{Joint Appearance and Shape Model Inference for the Segmentation of CT Images of the Cochlea}. 2020. (To be Submitted to IEEE Transactions on Medical Imaging)} % Award
    {\hypertarget{DWV+20}{[DWV+20]}} % Date(s)
    
%---------------------------------------------------------
  \cvhonor
    {Z. Wang, C. Vandersteen, \textbf{T. Demarcy}, [\ldots] and H. Delingette.  \textit{Deep Learning Based Metal Artifacts Reduction in Post-operative Cochlear Implant CT Imaging}. MICCAI, 2019.} % Award
    {\hypertarget{WVD+19}{[WVD+19]}} % Date(s)
      
%---------------------------------------------------------
  \cvhonor
    {E. T. Massuda, \textbf{T. Demarcy}, M. Hoen, [\ldots] and M. A. Hyppolito.  \textit{Electrode Migration in Patients with Straight Cochlear Implant Electrodes from Cone Beam Computed Tomography}. Cochlear Implants International, 20(5), p. 237-241, 2019.} % Award
    {\hypertarget{MDH+19}{[MDH+19]}} % Date(s)
    
%---------------------------------------------------------
  \cvhonor
    {F. Almairac, D. Fontaine, \textbf{T. Demarcy}, [\ldots]  and  C.  Raffaelli.   \textit{Motor  Cortexneurovascular Coupling: Inputs from Ultra High-frequency Ultrasound Imaging in Humans}. Journal of Neurosurgery, 131(5), p. 1347-1682, 2019.} % Award
    {\hypertarget{AFD+19}{[AFD+19]}} % Date(s)
    
%---------------------------------------------------------
  \cvhonor
    {F. Russo, M. Hoen, \textbf{T. Demarcy}, [\ldots] and I. Mosnier.  \textit{Pupillometry Assessment of Listening Effort in Adult Cochlear Implanted Patients}. Trends in Hearing, 2018. (In Revision)} % Award
    {\hypertarget{RHD+18}{[RHD+18]}} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\textbf{T. Demarcy}, C. Vandersteen, N. Guevara, [\ldots] and H. Delingette.  \textit{Automated Analysis of Human Cochlea Shape Variability from Segmented µCT Images}. Computerized Medical Imaging and Graphics, 59, p. 1-12, 2017.} % Award
    {\hypertarget{DVG+17}{[DVG+17]}} % Date(s)
    
%---------------------------------------------------------
  \cvhonor
    {C.  Vandersteen,  \textbf{T. Demarcy},  C.  Roger,  [\ldots]  and  N. Guevara. \textit{Impact of the Surgical Experience on Cochleostomy Location: A Comparative Temporal Bone Study Between Endaural and Posterior Tympanotomy Approaches for Cochlear Implantation}. European Archives of Oto-Rhino-Laryngology, 273(9), p. 2355-2361, 2015.} % Award
    {\hypertarget{VDR+15}{[VDR+15]}} % Date(s) 
       
%---------------------------------------------------------
  \cvhonor
    {N.  Schonbeck,  K.  Kvale,  \textbf{T.  Demarcy}, [\ldots] and  J.-F.  Berret.   \textit{Surfactant-Triggered  Disassembly of  Electrostatic  Complexes  Probed  at  Optical  and  Quartz  Crystal Microbalance Length Scales}. Langmuir, 30(19), p. 5620-5627, 2014.} % Award
    {\hypertarget{SKD+14}{[SKD+14]}} % Date(s)

%---------------------------------------------------------
\end{cvhonors}

%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
\cvsubsection{Peer-Reviewed Archived Conference \& Workshop Papers (1\textsuperscript{st} \& 2\textsuperscript{nd})}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvhonors}

%---------------------------------------------------------
  \cvhonor
    {\textbf{T. Demarcy}, C. Vandersteen, C. Raffaelli, [\ldots] and H. Delingette. \textit{Uncertainty Quantification of Cochlear Implant Insertion from CT Images}. Clinical Image-Based Procedures. Translational Research in Medical Imaging. CLIP 2016. Lecture Notes in Computer Science, 9958, p. 27-35, 2016.} % Award
    {\hypertarget{DVR+16}{[DVR+16]}} % Date(s)
    
%---------------------------------------------------------
  \cvhonor
    {D. Gnansia, \textbf{T. Demarcy},  C.  Vandersteen,  [\ldots]  and  N.  Ayache.\textit{Optimal  Electrode  Diameter  in  Relation  to  Volume  of  the  Cochlea}. European Annals of Otorhinolaryngology, Head and Neck Diseases, 133, p. S66-S67, 2016.} % Award
    {\hypertarget{GDV+16}{[GDV+16]}} % Date(s)
    
%---------------------------------------------------------
  \cvhonor
    {\textbf{T. Demarcy}, A. Saalbach, and J. Sénégas. \textit{Automated Organ Detection in Water-Fat Separated Magnetic Resonance Imaging}. Proceedings of the International Society for Magnetic Resonance in Medicine, 8(4), p. 4499, 2014.} % Award
    {\hypertarget{DSS14}{[DSS14]}} % Date(s)
    
%---------------------------------------------------------
\end{cvhonors}
\pagebreak
%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
\cvsubsection{Oral Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvhonors}

%---------------------------------------------------------
  \cvhonor
    {\textbf{T. Demarcy}, C. Vandersteen, D. Gnansia, [\ldots] and N. Guevara. \textit{Pre- and Postoperative Automatic Cochlear 3D Reconstruction Dedicated to Personalized Cochlear Implantation}. 14\textsuperscript{th} European Symposium on Pediatric Cochlear Implantation, 2019.} % Award
    {\hypertarget{DVG+19}{[DVG+19]}} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\textbf{T. Demarcy}, C. Vandersteen, D. Gnansia, [\ldots] and N. Guevara. \textit{Insertion Depth and Curvature Assessment of Cochlear Implantation}. 10\textsuperscript{th} International Symposium on Objective Measures in Auditory Implants, 2018.} % Award
    {\hypertarget{DVG+18a}{[DVG+18a]}} % Date(s)
    
%---------------------------------------------------------
  \cvhonor
    {\textbf{T. Demarcy}, C. Vandersteen, D. Gnansia, [\ldots] and N. Guevara. \textit{Cochlear Shape Variability from 987 Computed Tomography Images}. Association for Research in Otology, 41, 2018.} % Award
    {\hypertarget{DVG+18b}{[DVG+18b]}} % Date(s)
    
%---------------------------------------------------------
  \cvhonor
    {\textbf{T. Demarcy}, and M. Hoen. \textit{Magnetic Resonance Imaging and Cochlear Implant}. Latin American Meeting for Prevention and Treatment of Hearing Loss, 2018.} % Award
    {\hypertarget{MH18}{[MH18]}} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\textbf{T. Demarcy}, C. Vandersteen, D. Gnansia, [\ldots] and N. Guevera. \textit{Estimation of Postoperative Cochlear Implant Electrode-Array Position From Clinical Computed Tomography}. Annales Française d’Oto-Rhino-Laryngologie et de Pathologie Cervico-faciale, 2016.} % Award
    {\hypertarget{DVG+16}{[DVG+16]}} % Date(s)

%---------------------------------------------------------
\end{cvhonors}


%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
\cvsubsection{Media Coverage}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvhonors}

%---------------------------------------------------------
  \cvhonor
    {\textbf{T. Demarcy}, I. Pélisson, D. Gnansia, [\ldots] and N. Guevara.  \textit{Un modèle de reconstruction tridimensionnelle de la cochlée au service de l’implantation cochléaire}. Les Cahiers de l’Audition, 4, p. 36-40, 2019.} % Award
    {\hypertarget{DPG+19}{[DPG+19]}} % Date(s)
    
%---------------------------------------------------------

  \cvhonor
    {Métropole Mag N° 29, p. 20-22, September, 2019. (\headersocialstyle{\href{http://sophia-mag.com/wp-content/uploads/2019/09/MM29_24x33_BD.pdf}{\faLink~sophia-mag.com/wp-content/uploads/2019/09/MM29\_24x33\_BD.pdf}})} % Award
    {\hypertarget{MM}{[MM]}} % Date(s)

%---------------------------------------------------------

  \cvhonor
    {19/20, France 3 Provence Alpes Côte d’Azur, June 27, 2019. (\headersocialstyle{\href{https://france3-regions.francetvinfo.fr/provence-alpes-cote-d-azur/alpes-maritimes/nice/c-est-renaissance-laura-retrouve-audition-apres-20-ans-surdite-grace-implant-cochleaire-1691432.html}{\faLink~france3-regions.francetvinfo.fr/provence-alpes-cote-d-azur/alpes-maritimes/nice/c-est-renaissance-laura-retrouve-audition-apres-20-ans-surdite-grace-implant-cochleaire-1691432.html}})} % Award
    {\hypertarget{FR3}{[FR3]}} % Date(s)

%---------------------------------------------------------

  \cvhonor
    {Nice Matin, June 16, 2019. (\headersocialstyle{\href{https://www.nicematin.com/sante/premiere-mondiale-a-nice-deux-patients-atteints-de-surdite-severe-ont-retrouve-laudition-grace-a-un-implant-390152}{\faLink~www.nicematin.com/sante/premiere-mondiale-a-nice-deux-patients-atteints-de-surdite-severe-ont-retrouve-laudition-grace-a-un-implant-390152}})} % Award
    {\hypertarget{NM}{[NM]}} % Date(s)

%---------------------------------------------------------

  \cvhonor
    {UCA News, June 14, 2019. (\headersocialstyle{\href{http://web.univ-cotedazur.fr/contenus-riches/actualites/fr/une-collaboration-entre-le-chu-linria-et-oticon-donne-de-lespoir}{\faLink~web.univ-cotedazur.fr/contenus-riches/actualites/fr/une-collaboration-entre-le-chu-linria-et-oticon-donne-de-lespoir}})} % Award
    {\hypertarget{UCA}{[UCA]}} % Date(s)

%---------------------------------------------------------
\end{cvhonors}